\subsubsection{Risk 2: Not Enough Game Operators}

At our school, the AP Statistics class each year completes a carnival project, where they learn about expected values. Each group designs a game where they are expected to earn fake money from their game on the culminating Carnival Day, where students are given fake money to play the games. We are recruiting these students to be the game operators at our carnival because they have already designed games where they are expected to win.

In our strategic planning for the carnival, we identified a potential risk associated with our profit-sharing model for game operators. Given that the game operators were only entitled to 30\% of the profits they generated, there was a concern that this might not be a sufficient incentive for a large number of students to sign up as operators. This risk was further compounded by the fact that we, as the organizers, were absorbing all the financial risks associated with the event, including the upfront costs of the prizes.

The potential impact of this risk was significant. If we were unable to recruit a sufficient number of game operators, we would not have enough games at the carnival. This could lead to a less engaging and enjoyable experience for attendees, potentially impacting ticket sales and overall success of the event.

To mitigate this risk, we implemented a multi-faceted strategy. Firstly, we worked closely with the AP Statistics teachers to encourage more students to sign up as game operators, leveraging the alignment of the carnival project with their curriculum and emphasizing the little effort it would take to set up their previously made game. Secondly, we emphasized the non-financial benefits of participating as a game operator, such as the opportunity to apply their classroom learning in a real-world context, and the enjoyment of being part of a school-wide event. Lastly, we offered additional incentives such as complimentary food and beverages for game operators. Through these measures, we aimed to ensure a sufficient number of game operators to make the carnival a success.
