\section{Detailed List of Carnival Games}
\label{appendix:carnival_games}

\textit{Nerd Nerf Battle Turf}

This game involves nine balloons, each representing a different prize. Participants are given a Nerf gun and three chances to hit a balloon for a small prize, two chances for a medium prize, and one chance for a large prize.

\textit{Wheel of Fortune}

A classic carnival game where participants spin a fortune wheel. The outcome of the spin corresponds to different prize levels.

\textit{Chess vs. Wayne}

In this game, participants play a game of chess against an individual named Wayne. Winning the game yields a large prize, while losing still grants a small prize.

\textit{Las Vegas Casino}

This game consists of two parts. First, participants choose a color (red or black), then a roulette board is spun and a metal ball is dropped. If the ball lands on the chosen color, the participant advances to the next round. Landing on green yields an automatic big prize. Second, participants choose a cup from ten options (five filled with salt, five with sugar). Selecting a sugar-filled cup wins a small prize.

\textit{Steven the Dinosaur}

This is a card game where participants are given a card from 2-10, while the remaining eight cards are divided into two piles. Each turn, participants guess which card is in each pile. The game ends when an incorrect guess is made or all cards are correctly guessed. The number of correct guesses corresponds to different prize levels.

\textit{Chopsticks vs. Asian Dad}

In this game, participants must move rice from one bowl to another using chopsticks, aiming to beat Ruby's dad's time. This game tests the participant's dexterity and speed.

\textit{Tip Jar}

This game involves adding tickets to one of two jars, representing two characters from the recent Hunger Games movie: Coriolanus Snow and Finnick Odair. People can vote for their favorite character by adding tickets to the corresponding jar.

\textit{Papa's Ramenria}

This game involves guessing a customer's preferred soup base and side dish, and selecting four toppings for their ramen without choosing the one they're allergic to. Correct guesses advance the participant to the next level and yield various prizes, while incorrect guesses end the game.
